---
title: "Basic Linpe"
author: "Andrea Spano"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## The idea
Quite often I have found myself in the need of sharing a piece of data analysis with someone else. 

Sharing any analysis is usually about sharing 

* data:  basic format like `.csv` or `.RData` 
* analysis: an .Rmd file 

My idea is about sharing a single file: a `Rdata` file with the `.Rmd` file embedded into it so that any analysis becomes an _attribute_ of the data.

## Package `linpe`

Package linpe contains two main functions:

* link: link a `.Rmd` file to a data frame  object  
* perform: gets the  the `.Rmd` file from the data frame renders it in a thmp file

Any `.Rmd` linked to a data frame is known as a `linpe`.

## Examples
I want to create a simple `.Rmd` that analyses the `mtcars` data frame and I want to share iot with my friend `Akiro`


First I create a simple `.Rmd` file as:

<pre><code>
---
title: "Test linpe"
output: html_document
---
<pre><code>```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```</code></pre>
<pre><code>```{r , message = FALSE}
require(dplyr)
require(ggplot2)
```</code></pre>
Do something
<pre><code>```{r}
mtcars %>% 
  tbl_df() %>%
  group_by(cyl) %>%
  summarise(n = n(), mean_mpg = mean(mpg), sd_mpg = sd(mpg))
```</code></pre>
Plot something
<pre><code>```{r}
ggplot(mtcars, aes(disp, mpg)) + geom_point()
```</code></pre>
</code></pre>

and save it as `test-linpe.Rmd`


Then,  I `link` the `.Rmd`  to the `mtcars` data frame:


```{r}
require(linpe)
mtcars_linpe <- link (mtcars, file = "~/dev/linpe/test-linpe.rmd")
```



Finally, I save the mtcars_linpe as a `Rdata` object

```{r}
save(mtcars_linpe, file = "mtcars-linpe.Rdata"  )

```

and then sent the `mtcars-linpe.Rdata` to Akiro by email.

Once Akiro receives my email, he needs to:

Load the Rdata File

```{r}
load("mtcars-linpe.Rdata")
```


Check for the name of the `linpes` enclosed in the data frame:


```{r}
linpe(mtcars_linpe)
```

Render the `linpe` by issuing:

```{r, eval = FALSE}
perform(mtcars_linpe, "test-linpe")
```

As a result the `linpe` is rendered in Akiro's R installation and the results displayed in the default html viewer


